---
name: Tom L Jenkins
address: "Exeter, United Kingdom"
phone: +44 7880 950409
email: "Tom.L.Jenkins@outlook.com"
www: tomjenkins.netlify.app
twitter: 
github: Tom-Jenkins
position: PhD
date:
# output: vitae::hyndman
output:
  vitae::cv_document:
    template: hyndmantemplate_modified.tex
header-includes:
  - \geometry{left=1.8cm,right=1.8cm,top=1.9cm,bottom=1.9cm}
  - \definecolor{headcolor}{HTML}{3339FF}
editor_options:
  chunk_output_type: console
---

<!-- \titlespacing{\section}{0pt}{1.ex}{0.5ex} -->
\fontsize{12}{16}\sf


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = FALSE
)
library(tidyverse)
library(vitae)
```

```{r}
# Function to produce very basic table, no lines or headings
# https://github.com/robjhyndman/CV
baretable = function(tbl, digits = 0,
                      include.colnames = FALSE, include.rownames = FALSE,
                      hline.after = NULL,
                      size = getOption("xtable.size", NULL),
                      add.to.row = getOption("xtable.add.to.row", NULL),
                      longtable = FALSE,
                      ...) {
  xtable::xtable(tbl, digits = digits, ...) %>%
    print(
      include.colnames = include.colnames,
      include.rownames = include.rownames,
      hline.after = hline.after,
      comment = FALSE,
      tabular.environment = if_else(longtable, "longtable", "tabular"),
      floating = FALSE,
      size = size,
      add.to.row = add.to.row,
      sanitize.text.function = function(x) {
        x
      }
    )
}
```

\vspace{6pt}

# Profile

Scientist specialising in bioinformatics, data analysis and R programming. I have a broad range of experience and knowledge in evolutionary biology, geospatial analysis and data science. Previous projects include population genomics and whole genome sequencing of marine species, genome assembly and trait-association modelling, and predicting habitat suitability using machine learning.

\vspace{12pt}

# Employment

```{r, results = "asis"}
tribble(
  ~Start, ~End, ~Position, ~Place,
  "Apr 2022", "Present", "\\textbf{Bioinformatician \\& Software Developer}", "Animal and Plant Health Agency",
  "Feb 2021", "Mar 2022", "\\textbf{Senior Data Analyst / Advisor}", "Natural England",
  "Dec 2018", "Jan 2021", "\\textbf{Postdoctoral Research Associate}", "University of Exeter"
) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  select(Years, Position, Place) %>%
  baretable()
```

\vspace{12pt}

# Qualifications

```{r, results = "asis"}
tribble(
  ~Year, ~Degree, ~Subject, ~Grade, ~Institution,
  2018, "PhD", "Biological Sciences", "", "University of Exeter",
  2014, "MRes", "Biodiversity Informatics and Genomics", "Distinction", "Imperial Colleage London",
  2010, "BSc", "Marine Biology", "First Class Honours", "Swansea University"
) %>%
  select(Year, Degree, Subject, Institution) %>% 
  baretable()
```

\vspace{12pt}

# Computer Skills

```{r, results = "asis"}
tribble(
  ~Level, ~Skill,
  "Proficient", "\\textbf{R Programming, Linux , Geocomputation, MS Office}",
  "Competent", "\\textbf{GitHub, AWS, R Markdown, R Shiny, Leaflet.js, ECharts.js}",
  "Developing", "\\textbf{Nextflow, JavaScript}"
) %>%
  baretable()
```

\vspace{12pt}

# Selected Communication and Awards

```{r, results = "asis"}
tribble(
  ~Year, ~Award, ~Description,
  2022, "Interview", "Live interview on \\href{https://www.bbc.co.uk/news/uk-england-devon-61592108}{\\textit{BBC Radio Wales Drive}} to discuss published research on coral ",
  NA, NA, "habitat suitability modelling",
  2021, "Interview", "Pre-recorded interview on \\href{https://www.bbc.co.uk/news/uk-england-cornwall-56586904}{\\textit{BBC Radio Cornwall}} to discuss published research on",
  NA, NA, "red algae population genomics",
  2019, "Award", "British Ecological Society Research Grant (£5,000)",
  2018, "Talk", "Invited talk at Aquaculture Research Collaborative Hub UK Annual Conference",
  2018, "Award", "Heredity Fieldwork Grant (£1,284)"
) %>%
  baretable()
```

\vspace{12pt}

# Selected Publications

  * **Jenkins TL**, Stevens JR (2022). Predicting habitat suitability and range shifts under projected climate change for two octocorals in the north-east Atlantic. PeerJ 10, [e13509](https://doi.org/https://doi.org/10.7717/peerj.13509).
  * **Jenkins TL**, Guillemin M-L, Simon-Nutbrown C, Burdett HL, Stevens JR, Peña V (2021). Whole genome genotyping reveals discrete genetic diversity in north‐east Atlantic maerl beds. Evolutionary Applications 14, [1558–1571](https://doi.org/https://doi.org/10.1111/eva.13219).
  * Houston RD, Bean TP, Macqueen DJ, Gundappa MK, Jin YH, **Jenkins TL**, *et al*. (2020). Harnessing genomics to fast-track genetic improvement in aquaculture. Nature Reviews Genetics 21, [389–409](https://doi.org/https://doi.org/10.1038/s41576-020-0227-y).

